---
title: "LR Child Death : Descriptive Statistics"
author: "UA Research Team"
date: "March 28, 2019"
output: 
  html_document:
      toc: false
      number_sections: true
fontsize: 11pt
geometry: margin=1in
urlcolor: blue
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(results = 'asis',      # This is essential (can also be set at the chunk-level)
               comment = NA,
               prompt = FALSE,
               cache = TRUE,
               warning = FALSE,
               message = FALSE)
library(summarytools)
st_options(plain.ascii = FALSE,      
           style = "rmarkdown",      # This too
           footnote = NA,             # Avoids footnotes which would clutter the results
           subtitle.emphasis = FALSE  # This is a setting to experiment with - according to 
           )                                     # the theme used, it might improve the headings'
                                      # layout
```

```{r, echo=FALSE}
st_css()                              # This is a must; without it, expect odd layout,
```  


# Little Rock Child Death

This report was based on the child death data from Pulaski county between 2012-2019. This report shows the locations and a fitted spatial density map for the deaths reported in this time period and the descriptive statistics for the categorical predictors given in the dataset. 
Note that for almost all variables there are missing values (often reported as a blank cell or NA) and the descriptive tables also give an idea about their distribution. 

## Map of Incidents 

First we plot the incidents of child death on a map like a point process using the latitude and longitudes extracted by `ggmap`. I have shown only the final map and hidden the R codes. 

```{r, echo = F}
rm(list = ls())
require(devtools)
# devtools::install_github("dkahle/ggmap", ref = "tidyup")
# devtools::install_github("thomasp85/patchwork")
library(pacman)
p_load("sf"             # Spatial data objects and methods
       ,"mapview"        # Interactive Map Viewing
       ,"ggmap"          # ggplot2 addon for base maps
       ,"cowplot" 
       ,"spatstat"       # KDE and other spatial functions
       ,"raster"         # cell-based spatial operations
       ,"tidyverse"      # data manipulation framework
       ,"Hmisc"          # using cut2(  functions for ggplot legends
       ,"fitdistrplus"   # Distribution fitting functions
       ,"lubridate"      # Power tools for handling dates
       ,"tidycensus" 
       ,"lwgeom" 
       ,"Hmisc" 
       ,"hrbrthemes" 
       ,"gridExtra" 
       ,"spdep"          # KNN functions
       ,"foreach" 
       ,"doParallel" 
       ,"corrplot" 
       ,"ranger"         # randomforest implimentation      
       ,"glmnet"         # for Ridge and Lasso Regression
       ,"knitr"          # for kable table
       ,"kableExtra" 
       ,"FNN"            # KNN for CPS vs. NN plots
       ,"groupdata2" 
       ,"htmltools" 
       ,"viridis" 
       ,"viridisLite")
```

```{R, echo = F}
is.geocoded = T

if(is.geocoded == F){
  setwd("~/Data/LR-Child")
  child.death <- read.csv(file="Pulaski-child-death-data.csv",header=T,sep=",",
                    na.strings='NULL')
  child.death$Address = as.character(child.death$Address)
  geocoded_latlon <- geocode(child.death$Address,output="latlon")
  geocoded_latlon %>% head()
  
  child.death <- cbind(child.death,geocoded_latlon)
  colnames(child.death)
  write.csv(child.death, "Pulaski-child-death-data-geocoded.csv")
  is.geocoded = T
}
```



```{r, echo = F, fig.asp = 0.6}
setwd("~/Data/LR-Child")
colClasses = c("character","character","numeric",rep("character",2),rep("factor",10),rep("character",2),rep("numeric",2))

cd.gc <- read.csv(file="Pulaski-child-death-data-geocoded.csv",header=T,sep=",",colClasses = colClasses, nrows = 41, na.strings='NULL')

qmplot(lon, lat, data = cd.gc, geom = "point", maptype = "toner-lite", darken = .2, color = I("red"), legend = "topleft") +
  stat_density_2d(aes(fill = ..level..), geom = "polygon", alpha = .2, color = NA) +
  scale_fill_gradient2("Propensity", low = "white", mid = "yellow", high = "red", midpoint = 20)

```


### Yearly and weekly counts 

The stacked barplot below shows the death counts per year (distributed over the weeks).  

```{r, echo = F}
library(lubridate)
cd.gc$Incident.Date <- as.Date(cd.gc$Date.of.Death, format = "%m/%d/%Y" )
cd.gc$IncidentYear <- lubridate::year(ymd(cd.gc$Incident.Date))
cd.gc$IncidentWeek <- lubridate::week(ymd(cd.gc$Incident.Date))
library(dplyr)

crime.yearly.ct <- cd.gc%>% group_by(IncidentYear) %>%
  dplyr::summarise(count = n()) 

crime.weekly.ct <- cd.gc %>% group_by(IncidentYear, IncidentWeek ) %>%
  dplyr::summarise(count = n())
```

```{R, echo = F, fig.asp = 0.8}
library(ggplot2)
(weekly.plot <- ggplot(crime.weekly.ct, aes(x = IncidentYear, y = count))+
    geom_bar(aes(fill=IncidentWeek),stat = "identity",position = position_stack(reverse = TRUE)) +
    coord_flip() +
    theme(legend.position = "top")+ylab("Incident Count")+
    xlab("Years"))

# library(grid)
# library(gridExtra)
# p.comb<-grid.arrange(weekly.plot, yearly.plot, ncol = 1)

```


### Summary Statistics 

These were generated using the R package `summarytools`. Please note that the tables report the proportion and count in each category for the 10 categorical predictors provided in the data-set. There was a little bit of data cleaning, e.g. handling different labels ("F" and "Female" for Gender) and multiple values and multiple delimiters in preliminary accusation variable. 

I have not yet measured any association or dependence structure in this data. 

```{r, echo = T}
attach(cd.gc)
get.first.name <- function(cell){ 
  x<-unlist(str_split(as.character(cell), "\\;|,")) 
  return(x[1]) 
} 
cd.gc$Allegation.Prelim.Cause = sapply(Allegation.Prelim.Cause,get.first.name)

cd.gc$Gender = recode(cd.gc$Gender, F = "Female", M = "Male")

library(summarytools)
st_options(dfSummary.na.col = FALSE)
dfSummary(cd.gc[,6:15], plain.ascii = FALSE, style = "grid", 
          graph.magnif = 0.75, valid.col = FALSE, tmp.img.dir = "/tmp")
```


